The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-11-20 paper.tex
Additions to Section on Repeater Network

\sihui{
\subsection{Repeater networks}
}

>>>>

\sihui{
\subsection{Repeater networks}
Quantum repeaters are devices that distribute entanglement across a network, or teleport quantum states between nodes of a network. The purpose of such a quantum network is to communicate and process quantum information over long distances. While photons serve as great medium for information transfer, many implementations of photonic repeat network require some kind of nonlinear interactions involving cavities for entanglement distillation \cite{Briegel98} [BDCZ], quantum memories \cite{Duan01}, or feedforwarding \cite{bib:Azuma15}. The seminal work of Duan et al.~ \cite{Duan01}, in particular, uses atomic ensemble as quantum memories. Single photon interference then facilitates creation of entanglement between them. However, this makes the repeater node susceptible to interferometric instability which later schemes improve upon it by using two-photon interference instead \cite{Zhao07,YCZCS08,CZCS07}. Efforts in fault-tolerant quantum communication have led to error correction codes for photon loss and dark counts, that are common errors in repeaters \cite{bib:Muralidhara14,bib:Ewert16,bib:Ewert17,bib:Muralidharan17}]
}. These schemes can boost distances across which repeaters can act, or form tradeoffs by multiplexing, etc...
